% ****** Start of file aapmsamp.tex ******
%
%   This file is part of the AAPM files in the AAPM distribution for REVTeX 4-2.
%   Version 4.2a of REVTeX, January 2015
%
%   Copyright (c) 2015 American Association of Physicists in Medicine (AAPM).
%
%   See the AAPM README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aapmsamp
%  2)  bibtex aapmsamp
%  3)  latex  aapmsamp
%  4)  latex  aapmsamp
%
% Use this file as a source of example code for your aapm document.
% Use the file aapmtemplate.tex as a template for your document.
\documentclass[%
 aapm,
 mph,%
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
]{revtex4-2}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{maple}
\usepackage[utf8]{inputenc}
\usepackage[svgnames]{xcolor}
\usepackage{amsmath}
\usepackage{breqn}
\usepackage{textcomp}
\usepackage{subcaption}
\usepackage[settings]{markdown}


% \begin{document}
\lstset{basicstyle=\ttfamily,breaklines=true,columns=flexible}
\pagestyle{empty}
\DefineParaStyle{Maple Bullet Item}
\DefineParaStyle{Maple Heading 1}
\DefineParaStyle{Maple Warning}
\DefineParaStyle{Maple Heading 4}
\DefineParaStyle{Maple Heading 2}
\DefineParaStyle{Maple Heading 3}
\DefineParaStyle{Maple Dash Item}
\DefineParaStyle{Maple Error}
\DefineParaStyle{Maple Title}
\DefineParaStyle{Maple Ordered List 1}
\DefineParaStyle{Maple Text Output}
\DefineParaStyle{Maple Ordered List 2}
\DefineParaStyle{Maple Ordered List 3}
\DefineParaStyle{Maple Normal}
\DefineParaStyle{Maple Ordered List 4}
\DefineParaStyle{Maple Ordered List 5}
\DefineCharStyle{Maple 2D Output}
\DefineCharStyle{Maple 2D Input}
\DefineCharStyle{Maple Maple Input}
\DefineCharStyle{Maple 2D Math}
\DefineCharStyle{Maple Hyperlink}


\usepackage{gensymb}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{physics}
% \usepackage{mathtools}
% \usepackage{amsmath}
\usepackage{bm}% bold math
\usepackage[mathlines]{lineno}% Enable numbering of text and display math
\usepackage{multirow}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\modulolinenumbers[5]% Line numbers with a gap of 5 lines

\begin{document}
\noindent
\header{ENGR 120}
%\preprint{AAPM/123-QED}

\title[]{\underline{Fluid Mechanics: Lab 6} \\
Non-Invasive flow measurements: Vibrations and pipe flow}.% Force line breaks with \\

\author{Christian Emil Lorentsen}%
\author{Serafin Stauch}
\author{Bryan Saldivar}
\author{Xuan Zhao}

\affiliation{University of California, Merced}
\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified
\begin{abstract}
In this report we make use of accelerometers to determine flow rate through a pipe. We measure the acceleration (vibrations) of a pipe with a fluid flowing through it. We repeat this experiment for different materials, and flowrates. We use the statistical quantity $R^2$ to determine which axis of acceleration is best, and fit linearly to the data. Now, we can use the fit as a model, to predict flow rate through the pipe, non-invasively and obtain results of $(5.3\pm 3.3)m^3/hr$ for Copper, $(4.3\pm 2.9)m^3/hr$ for galvanized steel and $(6.2\pm 1.0)m^3/hr$ for PVC.

\end{abstract}

\maketitle
\linenumbers\relax % Commence numbering lines
\begin{quotation}
Measuring flow rate throguh pipes become increasingly important, as water resources seem to scarce. Having the ability to non-invasively measure flow rate, using only a simple accelerometer makes it possible to finely measure fluid flow in all sorts of small applications, such as in house hold applience and widely in industry. This can quickly and accuretely detect leaks and inefficiencies.

\end{quotation}
% \section{\label{sec:level1}Background}
% \input{Chapters/Background}
% \subsection{\label{sec:level2}Theory}
% \input{Chapters/Theory}
\section{\label{sec_level1}Method \& Setup}



\input{Chapters/Method&Setup}
% \newpage
\section{DATA AND RESULTS}
\input{Chapters/Results}


\subsection{Analysis}
\input{Chapters/Analysis}

\newpage
\section{DISCUSSION}
\input{Chapters/Discussion}

\section{CONCLUSION}
\input{Chapters/Conclusion}

{
\appendix
\section{Calculations}
\subsection{\label{app:python}Python code used to run the calculations and the numerical integration}
\input{Python}

}


\nocite{*}
\section*{\underline{Citations}}
\bibliography{aapmsamp}% Produces the bibliography via BibTeX.


\end{document}
%
% ****** End of file aapmsamp.tex ******
